Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-11-21 xrb2/paper.tex
Added 4e8 flame plots to temperature discussion

Figure~\ref{fig:compare_500Hz_abar} shows 3 different 500 Hz simulations with different initial temperature structures. The hottest model, $\tt{flame\_wave\_500\_3E8}$, has a faster propagating flame. It also appears to have a secondary burning region above the neutron star atmosphere layer (the atmosphere edge is located at $\sim 1.2\times 10^4$ cm). It is likely that a small amount of hot material broke through the top of the atmosphere.

@@

>>>>

Figure~\ref{fig:compare_500Hz_abar} shows 3 different 500 Hz simulations with different initial temperature structures. The hottest of the three models, $\tt{flame\_wave\_500\_3E8}$, has a faster propagating flame. It also appears to have a secondary burning region above the neutron star atmosphere layer (the atmosphere edge is located at $\sim 1.2\times 10^4$ cm). It is likely that a small amount of hot material broke through the top of the atmosphere.

@@

\begin{figure}[t]
	\centering
	\plotone{multiplot_3x1_time_series_enuc_late.png}
	\caption{\label{fig:4e8_stacked_enuc} Time series of the 500~Hz run $\tt{flame\_wave\_500\_4E8}$, with $T_{\mathrm{star}} = 4 \times 10^8~\mathrm{K}$, showing $\dot{e}_{nuc}$. This model burns so strongly that it is only run out to 40 ms; the snapshots shown here are at T = 30 ms, 35 ms, and 40 ms.}
\end{figure}

\begin{figure}[t]
	\centering
	\plotone{multiplot_3x1_time_series_abar_late.png}
	\caption{\label{fig:4e8_stacked_abar} Time series of the 500~Hz run $\tt{flame\_wave\_500\_4E8}$, with $T_{\mathrm{star}} = 4 \times 10^8~\mathrm{K}$, showing $\bar{A}$.}
\end{figure}
